{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
proofreading simulation and application part 1

	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$. For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following. Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.

@@

	To exploit the regularity of the curves of the spectra, we introduced different basis functions in Section \ref{bases} and demonstrated the importance of the truncation parameter $K$ for the estimation in Section \ref{Scalar_on_function_regression}. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC's, which is possibly affected by $K$, by ten-fold cross-validation using the prediction mean-squared error. The number of FPC's is in practice chosen by using the lowest number of FPC's that explains a specified amount of variability (cf. \cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (cf. \cite{Jolliffe_1982}). This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.\\

	This setup differs from the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high. This would avoid the heavy computations of validating the best value for $K$, which we will conduct in the simulation. To provide intuition in this approach, let 
	 \begin{equation}
	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} \left[ Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt \right]^2 + \lambda \int \left[D^m\beta(t)\right]^2 dt
	 \end{equation}

@@

    \subsection{Simulation setup}
	The simulation study follows \cite{Reiss_2007b} as a guideline. Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, are created that differ in their smoothness, to compare the introduced methods with differing true coefficient functions:
	\begin{equation}
    	f_1(t) = 401 \left[ 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) \right]
    \end{equation}
    \begin{equation}
    	\begin{split}
    		f_2(t) = 401  \Bigg[ & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)} \Bigg]
    	\end{split}
    \end{equation}

    The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}. The smooth function $f_1(t)$ follows \cite{Reiss_2007b} and its inner product $\langle NIR_{sim}, f_1 \rangle$ creates responses that are similar to the original octane numbers of the gasoline data set.

@@

		 Two different error-terms $\epsilon$ were created by first generating an i.i.d. standard normal error term and then multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios to test the methods with low and high amounts of noise. They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$	
		\begin{equation}
			\begin{split}
				Y_{1,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.9} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack \\
				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.6} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack
			\end{split}
		\end{equation}

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations, using the two true coefficient functions and the two error terms. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $nharm$ FPC's for $nharm \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was smoothed with the respective basis function specification. The obtained Eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
		\begin{equation}
			\begin{split}
				\hat{\xi}_{i}^{m, \mathcal{H},L} & =  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\tilde{\nu}^{m, L, \mathcal{T}} }\mathrm{d}s) 
			    \approx \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} d_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
			\end{split}
		\end{equation}

		with truncation parameter $L$. In total, 5000 repetitions were conducted for each set of simulations.

	\subsection{Results}	
	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in Appendix \ref{Tables_sim} and \ref{Estimates_sim}. 
	\subsubsection{Basis Expansion Regression}
	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform FLR. Examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.

	\paragraph{Monomial Basis}
	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability. For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this coefficient function. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10} provide evidence. It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries. This weakness is especially pronounced in the MSPE for $f_2,Y_1$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratio. 
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
	Function $f_1$ requires 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis. It still performs the worst for $f_1$. An explanation might be its exaggerated behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ (\hyperref[basis_expansion_1_1]{ADD} and \hyperref[basis_expansion_1_2]{ADD}), which is especially pronounced for the lower signal-to-noise ratios. For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio. For $f_2$, the B-spline basis outperforms the monomial basis but comes second to the Fourier basis. While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ((\hyperref[basis_expansion_2_1]{ADD} and \hyperref[basis_expansion_2_2]{ADD})).
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio. With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$. The Fourier basis functions perform the best for each setup for the basis expansion regression. Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$ does at least not display any erratic jumps. Second, both functions feature periodic behavior. Third, $f_2$ does have the same value at the start- and the end of the interval lending itself to a periodic representation.	\\

	\subsubsection{Functional Principal Component Regression}
		The model used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. In addition to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function. But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's. This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.

	\paragraph{Monomial Basis}
	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$). In  $f_2$ we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions. The monomial basis shows the weakest performance for all three basis functions in each setting for all $n_{FPC}$.
	\vspace{-0.2cm}

@@

	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered. An hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting. To examine this further, additional simulations were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$ (LINK TO APPENDIX). As in the simulation study we can find potential signs of overfitting for all setups and both choices of $L$. The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be a first sign of a too high $L$ and subsequent undersmoothing. Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$). The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's which might indicate beneficial attributes of the lower truncation parameters used in the main simulation.

@@

		\subsubsection{Functional Principal Component Regression}
		The best performance for all numbers of FPC's was achieved with the Fourier Basis, as for the FPCR in the simulation study. In contrast to the simulation study, no evidence of overfitting was found for the best basis choices in any of the three bases. The MSPE for the optimal specification appears to be strictly decreasing in the number of FPC's. As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears to be the case that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed. Differing from the simulation study, the number of basis functions is steadily increasing for the monomial basis. The behavior for the B-spline basis is similar to the one reported in the simulation study (basis functions increasing in $n_{FPC}$).

@@

	\paragraph{Insights from Simulation cannot be Extended to More General Functions}
	\vspace{-0.2cm}

@@

	\paragraph{Input from Physics Analysis}
	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates. For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with a high predictive power for the octane value. This could guide, for example, the construction of a B-spline basis that focuses on the relevant parts of the spectrum by using a vector of knots founded by field expertise. Alternatively, it could be used to link specific principal components to compounds which would be interesting for the interpretation of estimates.
	\vspace{-0.2cm}

>>>>

	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$. For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following. Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.

@@

	To exploit the regularity of the curves of the spectra, we introduced different basis functions in Section \ref{bases} and demonstrated the importance of the truncation parameter $K$ for the estimation in Section \ref{Scalar_on_function_regression}. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $L$ as well as the number of FPC's, which is possibly affected by $L$, by ten-fold cross-validation using the prediction mean-squared error. The number of FPC's is in practice chosen by using the lowest number of FPC's that explains a specified amount of variability (cf. \cite{kokoszka_introduction_2017}), which might not be optimal since FPC's with smaller Eigenvalues may have greater influence on the prediction (cf. \cite{Jolliffe_1982}). This might apply to this simulation too since certain Eigenfunctions could correspond to certain chemical combinations and overtones in the absorption bands of the spectrum that could have high predictive power, but explain only little variability in the NIR curves shown in Appendix \ref{NIR}.\\

	This setup differs from the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $L$ sufficiently high. This would avoid the heavy computations of validating the best value for $L$, which we will conduct in the simulation. To provide intuition in this approach, let 
	 \begin{equation}
	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} \left[ Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt \right]^2 + \lambda \int \left[D^m\beta(t)\right]^2 dt
	 \end{equation}

@@

    \subsection{Simulation setup}
	The simulation study follows \cite{Reiss_2007b} as a guideline. Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, that differ in their smoothness are created to compare the introduced methods with differing true coefficient functions:
	\begin{equation}
    	f_1(t) = 401 \left[ 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) \right]
    \end{equation}
    \begin{equation}
    	\begin{split}
    		f_2(t) = 401  \Bigg[ & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)} \Bigg]
    	\end{split}
    \end{equation}

    The function $f_2(t)$ was generated by referring to \cite{cardot_bumpyfunction_2002} while function $f_1(t)$ directly follows \cite{Reiss_2007b}. 
    %and its inner product $\langle NIR_{sim}, f_1 \rangle$ creates responses that are similar to the original octane numbers of the gasoline data set.

@@

		 Two different error-terms $\epsilon$ were created by first generating an i.i.d. standard normal error term and then multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios of the responses to test the methods with low and high amounts of noise in the responses. They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$	
		\begin{equation}
			\begin{split}
				Y_{1,f} & = \langle NIR, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.9} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack \\
				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{sim}, f\rangle)}{0.6} - var(\langle NIR_{sim}, f\rangle)\biggr\rbrack
			\end{split}
		\end{equation}

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations, using the two true coefficient functions and the two error terms. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic B-spline basis-function $\{5,6,...,18\}$ and Fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach.
		% For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
		To obtain valid out of sample properties for the FPCR, within each of the ten ten-fold cross-validation splits, we first calculate the first $n_{FPC}$ FPC's for $n_{FPC} \in \{2,3,4\}$ of the training set $\mathcal{T}$, which was prior smoothed with the respective basis function specification. The obtained Eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation
		\begin{equation}
			\begin{split}
				\hat{\xi}_{i}^{m, \mathcal{H},L} & =  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\tilde{\nu}^{m, L, \mathcal{T}} }\mathrm{d}s) 
			    \approx \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{L} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k = 1}^{L} d_{k}^{m, \mathcal{T}} \phi_{k}(s)\right)} \mathrm{d}s \\
				 &\approx \sum_{j = 1}^{L} \left[ a_{i,j}^{\mathcal{H}}\sum_{k = 1}^{L}  d_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
			\end{split}
		\end{equation}

		with truncation parameter $L$. In total, 5000 repetitions were conducted for each specified model, basis system and basis function. The models are denoted as a combination of the function $f \in \{f_1(t), f_2(t)\}$	and created responses $Y \in \{Y_1, Y_2\}$.

	\subsection{Results}	
	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in Appendix \ref{Tables_sim} and \ref{Estimates_sim}.

	\subsubsection{Basis Expansion Regression}
	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform scalar-on-function regression. Examining the results, it appears that the cross-validated MSPE inherits a convex nature in the increasing basis functions.

	\paragraph{Monomial Basis}
	Due to the in the number of monomial basis functions increasing collinearity, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability. For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$ where it shows a better performance than B-splines for this assumed true coefficient function. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In case of $f_2$, this basis shows the weakest performance out of all basis, for which the plots in figure \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide evidence. It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries. This weakness is especially pronounced in the MSPE for $f_2,Y_1$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratio. 
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
	Function $f_1$ requires 5(4) B-spline basis functions for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis and shows the worst performance of the three basis. An explanation might be its overripe behavior at the boundaries and the exaggeration of the peculiarities of $f_1$ ( figure \ref{basis_expansion_1_1} and \ref{basis_expansion_1_2}), which is especially pronounced for the lower signal-to-noise ratio. For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratio. The B-spline basis outperforms the monomial basis in $f_2$, but comes second to the Fourier basis. While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ( figure \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2}). With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise using $\hat{\beta}(t)$.
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio. As for the B-splines basis functions, the simulation chooses a smaller number of basis functions for the noisy responses and a higher number for the high signal-to-noise responses. The Fourier basis functions perform the best for each setup for the basis expansion regression. Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$ does at least not display any erratic jumps. Second, both functions feature periodic behavior. Third, $f_2$ does have the same value at the start- and the end of the interval lending itself to a periodic representation.	\\

	\subsubsection{Functional Principal Component Regression}
		The model used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. In addition to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated Eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to expand the function. But since the FPCR is ultimately estimated with a linear model with the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE, nor any clear relationship can be observed between the number of basis function and the number of FPC's. This might be because the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions regarding this within this simulation study. Therefore, we will limit ourself to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account (same number of basis functions for the different signal-to-noise ratios). A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the noise in the responses at all.

	\paragraph{Monomial Basis}
	For $f_1$, the cross-validated MSPE is decreasing in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} \in \{2, 3, 4 \}$). In  $f_2$ we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions. The monomial basis shows the weakest performance for all three bases in each setting for all $n_{FPC}$.
	\vspace{-0.2cm}

@@

	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered. An hypothesis for this is that the dependency between the truncation parameter $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is too complex to capture in our setting. To examine this further, additional simulations ( section \ref{Tables_sim_additional}) were conducted for B-spline basis functions with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$. As in the simulation study we can find potential signs of overfitting for all setups and both choices of $L$. The additional simulations revealed evidence that there might exist a relationship from $n_{FPC} = 3$ onwards: For $n_{FPC} \in \{3, \dots, 7 \}$, the 10-fold cross-validated MSPE is always lower for 50 than for 70 basis functions which might be a first sign of a too high $L$ and subsequent undersmoothing. Following this, it seems that once a sufficient number of basis functions is used to expand the curves, the FPCR performs better using a more conservative number of basis functions (here $L = 50$). The settings $f_1,Y_2$ and $f_2,Y_2$ perform worse for these high number of basis functions compared to the main simulation, while $f_1,Y_1$ and $f_2,Y_1$ show a stronger performance than in the main simulation study, although the signal-to-noise ratios of the responses are not affecting the construction of the FPC's. This might indicate beneficial attributes of the lower truncation parameters in settings with low signal-to-noise responses.

@@

		\subsubsection{Functional Principal Component Regression}
		The best performance for all numbers of FPC's was achieved with the Fourier Basis, as for the FPCR in the simulation study. In contrast to the simulation study, no evidence of overfitting was found for the best basis choices in any of the three bases. The MSPE for the optimal specification appears to be strictly decreasing in the number of FPC's. As for the simulation study, the interpretation of the results with respect to the chosen basis is difficult: Referring to the plotted estimates $\hat{\beta}(t)$ in figure  \ref{FPCR2_estimate_appl}, \ref{FPCR3_estimate_appl} and \ref{FPCR4_estimate_appl}, it appears to be the case that the higher $n_{FPC}$ is, the more similar behavior of the estimate $\hat{\beta}(t)$ can be observed. Differing from the simulation study, the number of basis functions is steadily increasing for the monomial basis. The behavior for the B-spline basis is similar to the one reported in the simulation study (basis functions increasing in $n_{FPC}$).

@@

	\paragraph{Insights from Simulation cannot be Extended to More General Functions}
	As described, the properties of the two used functions $f \in \{f_1(t), f_2(t)\}$ influence the results. Although the resulting MSPE and visual inspection provided some evidence to support the hypothesis that the true coefficient function of $NIR$ might be similar to $f_2$, several other factors that were not asserted could also have caused this. Therefore, this simulation is not sufficient to base a reasonable claim concerning more general true coefficient functions on it.
	\vspace{-0.2cm}

@@

	\paragraph{Input from Physics Analysis}
	\vspace{-0.2cm}
